Assignment II: Adopting an Open Science Workflow

### 2024-07-11 doc/presentation_mine.qmd
- Converted trr266_logo.eps to trr266_logo.pdf using Ghostscript for compatibility with XeLaTeX. - Updated beamer_theme_trr266.sty to reference the new PDF logo file.

---
title: "Assignment II: Adopting an Open Science Workflow"
author: "Melisa Mazaeva"
institute: "Accounting Reading Group – Summer 2024"
date: today
fontsize: "9pt"
pdf-engine: xelatex # pdflatex creates rastered fonts
format: 
  beamer:
    slide-level: 3
    number-sections: true
    toc: false
header-includes:
- \usepackage{booktabs} 
- \usepackage{threeparttable}
- \usepackage{graphicx}
- \usepackage{etoolbox}
- \AtBeginEnvironment{verbatim}{\fontsize{7}{7}\selectfont}  # This sets the font size for verbatim environments
#- \input{beamer_theme_trr266.sty}
bibliography: references.bib
biblio-style: apsr
---

>>>>

---
title: "Assignment II: Adopting an Open Science Workflow"
author: "Melisa Mazaeva"
institute: "Accounting Reading Group – Summer 2024"
date: today
fontsize: "9pt"
pdf-engine: xelatex # pdflatex creates rastered fonts
format: 
  beamer:
    slide-level: 3
    number-sections: true
    toc: false
header-includes:
- \usepackage{booktabs} 
- \usepackage{threeparttable}
- \usepackage{graphicx}
- \usepackage{etoolbox}
- \AtBeginEnvironment{verbatim}{\fontsize{7}{7}\selectfont}  # This sets the font size for verbatim environments
- \input{beamer_theme_trr266.sty}
bibliography: references.bib
biblio-style: apsr
---
